Prediction of the 2020 Presidential Election

### 2020-11-02 outputs/paper/paper.Rmd
w or l?
first data commit (checking length)

Our data is of penguins (Figure \@ref(fig:bills)).

@@

>>>>

As previously mentioned, our data is from two different datasets; the Democracy Fund + UCLA Nationscape Wave 50 dataset, and the 2018 1-year American Community Survey (ACS) dataset. They each contain both qualitative and quantitative data. In regard to the Nationscape Wave 50 dataset, a few of its strengths are the variety in variables considered, and the quality of the survey responses. With respect to its weaknesses, it is likely that the data contains sampling error and/or coverage error. One of the various strengths of the  ACS dataset is its ability to be customized with pre-specified (or pre-selected?) variables and sample size before download. Although there is a wide range of variables to choose from, being able to select only those which we needed made the exploratory data analysis process much more manageable than it could have otherwise been (with all possible variables). Furthermore, since sample size can be pre-specified to a limit of about 3.2 million people, the larger the sample size is set to, the greater the odds that the target population is represented with the data. In terms of weaknesses of the ACS dataset, there are none all that significant. Some minor concerns, however, are potential measurement error, processing error, and/or adjustment error in the data.
  The Democracy Fund + UCLA Nationscape is "one of the largest public opinion surveys ever conducted -- interviewing people in nearly every county, congressional district, and mid-sized U.S. city in the leadup to the 2020 election." Consequently, interviewing "roughly 6,250 per week" was part of the survey methodology employed by Nationscape. As such, the Nationscape Wave 50 dataset contains results for 6,479 interviews conducted during the week of June 25-July 1, 2020. It can be accessed by visiting https://www.voterstudygroup.org/publication/nationscape-data-set and submitting a request to access the data. By providing your full name and email address, you will then be emailed a link to the page where it can be downloaded. 
  At first glance of the Wave 50 data, we noted that it contains 265 variables. This is noteworthy because it allows a more complete picture of voter attitude to be derived from the data compared to if there were less variables. Another strength of this dataset is the overall quality of responses from those surveyed. More specifically, the data does not contain any duplicate records, inappropriate entries, or poor entries (e.g. typos, misspellings); hence, making it easier to work with. This high quality of survey responses can be partially attributed to the fact that "Nationscape samples are provided by Lucid, a market research platform that runs an online exchange for survey respondents." What is more, the individuals belonging to the sample are required to "complete an attention check before completing the [online] survey." With this method of sample selection, along with the precaution taken to ensure their attentiveness, it is unlikely for survey respondents to submit low-quality responses. 
  The main weakness of the Nationscape Wave 50 dataset is the likelihood that it includes sampling error and/or coverage error. While the goal of the Nationscape survey is to determine American voter attitudes, making inferences based only on the Wave 50 dataset would result in sample bias. This is because the target population is all American citizens age 18 years and older, whereas the sample frame is Lucid's online exchange for survey respondents, and the sample is a set of 6,479 individuals from said online exchange which match "a set of
demographic criteria." It is very unlikely that a sample of 6,479 American citizens during a single week is representative of American voter attitudes as a whole. This may lead one to wonder why Nationscape chose to use the described sampling approach. Apart from the fact that the survey was conducted every week, the reason is trade-offs. For example, although there is potential coverage error in the data--a common result of online surveys--some trade-offs are a lesser rate of non-response, lower cost, convenience and accuracy. Whilst on the topic of non-response, it is worth mentioning that the variable with greatest amount of non-response in the Wave 50 dataset is household income at rouhly 5.5%. Nonetheless, this is a much smaller percentage of non-response in household income than is typically seen in political surveys, and Nationscape handles it by not weighting income for non-respondents. Similarly, a statement from Nationscape in its "Representativeness Assessment" implies an overall lack of concern for non-response in the data, as "previous evaluations of the samples Lucid provides have found them to be of high quality." 
  The last aspect of the Nationscape Wave 50 dataset to be considered is the survey questionnaire itself. Strengths of the questionnaire include its structure, the design and wording of the questions being asked, and the variety of choices for closed-ended questions. As to the structure of the questionnaire, it contains an extensive amount of questions from which differing political views can be revealed. Furthermore, the survey questions are asked in an order that does not influence the answer of respondents to subsequent questions. 
In terms of the design and wording of the questions, they are closed-ended, and avoid the use of tricky wording. This is a strength of the questionnaire because it makes comparing the responses of individuals and thus, statistical analysis, much simpler than it would be with open-ended questions and/or troublesome language. The diverse number of options available to select as answers to the questions is a strength of the questionnaire because they are both mutually exclusive and exhaustive; hence, ensuring survey respondents are able to answer every question. With respect to weaknesses of the questionnaire, it seems that there are none other than its sheer length.

@@

estimate_votes %>% mutate(status = if_else(predicted_vote>=0.50,"win","loss")) %>% group_by(status) %>% tally(
)
